Computing Entropies With Nested Sampling

### 2017-07-09 paper/ms.tex
Discuss tolerance

>>>>

By default, {\tt postprocess.py} estimates the depth with a tolerance of
$L=10^{-3}$. This value can be changed by calling the {\tt postprocess}
function with a different value of its argument {\tt tol}. E.g.,
{\tt postprocess.py} can be edited so that its last line is
{\tt postprocess(tol=0.01)} instead of {\tt postprocess()}.
